Project 2

### 2018-10-02 Project2/report/Project2.tex
Lacks final statement in abstract and conclusion. Also needs proof reading

Reviewing [fig:\ref{fig:fig4}] it is clear that increasing $\omega_{r}$ in turn makes the potential become increasingly confined as explained with [fig\ref{fig:fig5}], this is seen on the location of the probability function in the plot. Removing the Coulomb potential has the same effect as confining the electrons in a very strong potential since the significance between interaction with the potential and between the electrons is reduced.

>>>>

Reviewing [fig:\ref{fig:fig4}] it is clear that increasing $\omega_{r}$ in turn makes the potential become increasingly confined as explained with [fig:\ref{fig:fig5}], this is seen on the location of the probability function in the plot. Removing the Coulomb potential has the same effect as confining the electrons in a very strong potential since the significance between interaction with the potential and between the electrons is reduced.
